Individual Stellar Haloes of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-11-15 draft/paper1_v15.tex
Final edits

\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halos in Massive Galaxies]{Individual Stellar Halos of 
	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
% \title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
% 	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

@@

    \song{
    The stellar halo of massive galaxy can extend to several hundreds of kilo 
    parsecs and provide important fossil record of galaxy assembly.
    Using the wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) images 
    from the Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP), we study 
    the stellar halos of a sample of $\sim7000$ massive galaxies at 
    $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$ by tracing their  
    surface mass density profiles to 100 kpc individually. 
    The stellar halo of massive galaxy exhibit higher intrinsic diversity in their 
    outer surface density profile and higher ellipticity than the inner region. 
    We find that more massive galaxy on average shows more prominent outer stellar 
    halo with shallower surface density profiles.
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients.
    }
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events.
    \song{
    These results also emphasize the importance of accounting for the the extended 
    stellar halos of massive galaxies when estimating their stellar masses. 
    Shallow image or inadequate profile model often leads to significantly 
    underestimated masses.
    We provide surface mass surface mass density profiles to facilitate comparisons 
    with predictions from hydrodynamic simulations and other observations.
    }

@@

\begin{keywords}
    galaxies: elliptical and lenticular, cD --
    galaxies: formation --
    galaxies: photometry -- 
    galaxies: structure -- 
    galaxies: surveys
\end{keywords}

@@

    \song{
    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
    ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}): A rapid growth phase at high-redshift that 
    is dominated by intense dissipative \textit{in situ} star formation (e.g.
    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
    is driven by non-dissipative processes such as dry mergers 
    (e.g. \citealt{Naab2006, Khochfar2006}), especially the minor ones 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
    mass accreted in the second phase (\textit{ex situ} component) should increase 
    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    }
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
%% ------------------------------------------------------------------------------------ %%

    \song{
    Given the success of the ``two-phase'' scenario in explaining the properties of 
    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
    this model with additional observations, in particular, the detailed surface 
    mass density profiles of low redshift massive galaxies. 
    }
    Early studies based on one-dimensional light profiles found that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    However, recently, detailed empirical comparison of surface brightness profiles 
    revealed a more complicated situation showing that ETGs belong to two families, 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    \song{
    Until now, deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is not trivial to map the low surface
    brightness outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
    Some of these measurements are based on image stacking method (e.g. 
    \citealt{Tal2011, dSouza2015}) that suffers from several systematics. 
    The number of very massive galaxies is also very limited in the local universe.
    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
    luminosity) within 108 Mpc.
    }

    \song{
    Besides the mass density profiles, the radial profile of ellipticity also 
    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
    If the stellar halos of massive galaxies are indeed dominated by accreted 
    stars, their ellipticities could be systematically different with the inner 
    regions and contain clues about the assembly history of massive galaxies 
    (e.g. average time since last merger, average merger mass ratio).
    These issues have not been fully explored in both simulation and observation.
    Certain simulation predicts more massive ETG should have rounder shape
    (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
    elongated haloes (e.g. \citealt{Li2017}).  
    On the observational side, constraints are only available from few works 
    using either image stacking method (e.g. \citealt{Tal2011, dSouza2015}) or 
    small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
    }

    \song{
    In this paper, we take advantage of the high--quality and deep images from the 
    Hyper Suprime-Cam (HSC) Subaru Strategic Program \citep[SSP,][]{HSC-DR1} 
    (see \S~\ref{ssec:hsc} for details) to characterize the light profiles of 
    massive galaxies out to 100 kpc. 
    }
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

    In this paper, we use this sample to 
    (a) reliably estimate individual surface mass density (\mden{}) profiles of 
    massive galaxies out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications in terms of evaluating the high mass end of the 
    galaxy stellar mass function (SMF). 
    In a second paper in this series, we will investigate the environmental 
    (dark matter halo mass) dependence of the sizes of massive ETGs 
    (Huang\etal in prep.).

    This paper is organized as follows. 
    \S~\ref{sec:data} presents our data and initial sample selection. 
    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    \S~\ref{sec:mstar} describes how we estimate stellar mass.
    \S~\ref{sec:final} summaries the final sample selection procedure. 
    Our main results are presented in \S~\ref{sec:result} and discussed in 
    \S~\ref{sec:discussion}. 
    \S~\ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    Halo mass is defined as $M_{\rm 200b}$ as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirts of massive 
    brightest cluster galaxy (BCG)
    hints at a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component trace different scales of a single, smooth, and continuous 
    distribution.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
            \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            It is a very conservative estimate of the region that we can not reliable 
            extract 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the mean ellipticity used for the 
            final isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
    Miyazaki in~prep.), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 110$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
    the $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
    statistical studies of the surface brightness profiles of massive galaxies out to 
    their distant outskirts.  
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC Data Processing}
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

    The pixel scale of the combined images is $0.168$\asec{}. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the \texttt{coadd} level. 
    First, \texttt{hscPipe} performs object detection on \texttt{coadd} images in 
    each band independently and records the flux peak and the above-threshold region 
    (referred as a \texttt{footprint}) for each source. 
    Next, \texttt{footprints} and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} performs forced photometry 
    on the \texttt{coadd} image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors
    at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).

>>>>

\documentclass[fleqn,usenatbib]{mnras}

@@

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
\newcommand{\susan}[1]{\textcolor{Bittersweet}{\textbf{#1}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Haloes in Massive Galaxies]{Individual Stellar Haloes of 
	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

@@

    \song{
    Massive galaxies display extended light profiles that can reach several 
    hundreds of kiloparsecs. 
    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
    haloes of a sample of $7000$ massive galaxies at $z=0.4$. 
    The depth of the HSC data enables us to measure surface mass density profiles 
    to 100 kpc for individual galaxies without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles than smaller galaxies.  
    When this extended light is not properly accounted for (because of shallow imaging 
    and/or inadequate profile modeling), the derived stellar mass function can be 
    significantly underestimated at the high mass end.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    }
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at a later time from a series of merging events. 
    We provide surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

@@

\begin{keywords}
    galaxies: elliptical and lenticular, cD --
    galaxies: formation --
    galaxies: photometry -- 
    galaxies: structure -- 
    survey 
\end{keywords}

@@

    \song{
    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
    `two-phase' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}): a rapid growth phase at high-redshift that 
    is dominated by intense dissipative \textit{in situ} star formation (e.g.
    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
    is driven by non-dissipative processes such as dry mergers 
    (e.g. \citealt{Naab2006, Khochfar2006}), with an important role played by 
    minor mergers 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
    mass accreted in the second phase (the \textit{ex situ} component) should increase 
    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    }
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly with galaxy mass, reaching
    $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ 
    (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at the high mass end.}. 
%% ------------------------------------------------------------------------------------ %% 
    \song{
    Given the success of the `two-phase' scenario in explaining the properties of 
    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
    this model with additional observations, in particular, the detailed surface 
    mass density profiles of low-redshift massive galaxies. 
    }
    Early studies based on one-dimensional light profiles found that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central regions) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    A more recent study of the surface brightness profiles of ETGs 
    revealed that ETGs belong to two families: 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better described by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b}, further suggesting a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly histories.

    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}), as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    \song{
    To date, large samples of massive galaxies with deep imaging have been lacking. 
    Even in the nearby universe, it is not trivial to map the low surface
    brightness outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
    Some of these measurements are based on image stacking methods (e.g. 
    \citealt{Tal2011, dSouza2015}). 
    The number of very massive galaxies is also very limited in the local universe.
    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
    luminosity) within 108 Mpc.
    }

    \song{
    In addition to mass density profiles, the radial profile of ellipticity also 
    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
    If the stellar haloes of massive galaxies are indeed dominated by accreted 
    stars, their ellipticities could be systematically different with the inner 
    regions and may contain clues about the assembly history of massive galaxies 
    (e.g. average time since last merger, average merger mass ratio).
    These issues have not been fully explored in both simulation and observation.
    Certain simulation predicts that a more massive ETG should have rounder shape
    (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
    elongated haloes (e.g. \citealt{Li2017}).  
    On the observational side, constraints are only available from a few works 
    that use either an image stacking method (e.g. \citealt{Tal2011, dSouza2015}) 
    or a small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
    }

    \song{
    In this paper, we take advantage of the high-quality deep images from the 
    Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP) \citep[SSP,][]{HSC-DR1} 
    (see \S~\ref{ssec:hsc} for details) to characterize  the light profiles of 
    massive galaxies out to 100 kpc. 
    }
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
    %\susan{Note that MNRAS requirement is to use British spelling; however, 
    %they also prefer the -ize variant of word such as recognize, criticize, 
    %minimize, emphasize, organize, ionize, polarize, parametrize (etc.).}

    We use this sample to 
    (1) reliably estimate individual surface mass density (\mden{}) profiles of 
    massive galaxies out to 100 kpc, 
    (2) investigate the dependence of their outer stellar haloes on total stellar 
    mass, and 
    (3) examine the implications in terms of evaluating the high mass end of the 
    galaxy stellar mass function (SMF). 
    In a second paper in this series (Huang \etal in prep.), we will investigate 
    the environmental (dark matter halo mass) dependence of the sizes of massive 
    ETGs (Huang\etal in prep.).

    This paper is organized as follows. 
    \S~\ref{sec:data} presents our data and initial sample selection. 
    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    \S~\ref{sec:mstar} describes how we estimate stellar mass.
    \S~\ref{sec:final} summarizes the final sample selection procedure. 
    Our main results are presented in \S~\ref{sec:result} and discussed in 
    \S~\ref{sec:discussion}. 
    \S~\ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    Halo mass is defined as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

    We emphasize that in this work we do not attempt to disentangle the 
    galaxy light from any `intra-cluster' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirts of massive 
    brightest cluster galaxy (BCG)
    hints at a kinematically separated intra--cluster light (ICL) component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate it photometrically.
    Moreover, both the stellar halo of the main galaxy and the ICL component carry 
    important information regarding the assembly history of the central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component trace different scales of a single, smooth, and continuous 
    distribution.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            \textbf{Left}: Example of the 1-D surface brightness and ellipticity 
            profile of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
            \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shading highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            Because it is a very conservative estimate of the region, we cannot reliably 
            extract a 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the mean ellipticity used for the 
            final isophote. 
            \textbf{Right}: The 3-colour image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
    Miyazaki in~prep.), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in five broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 110$ deg$^2$ in all five bands to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic 
    surveys 
    [e.g.\ Sloan Digital Sky Survey (SDSS)/Baryon Oscillation Spectroscopic Survey 
    (BOSS): \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
    Galaxy And Mass Assembly (GAMA): \citealt{Driver2011}, \citealt{Liske2015}].
    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
    the $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
    statistical studies of the surface brightness profiles of massive galaxies out to 
    their distant outskirts.  
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low-redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We therefore use $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC data processing} 
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modelling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

    The pixel scale of the combined images is $0.168$\asec{}. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the \texttt{coadd} level. 
    First, \texttt{hscPipe} performs object detection on \texttt{coadd} images in 
    each band independently and records the flux peak and the above-threshold region 
    (referred as a \texttt{footprint}) for each source. 
    Next, \texttt{footprints} and peaks from different bands are merged before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands. (For most galaxies in this work, the reference band is 
    the $i$-band.) 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} performs forced photometry 
    on the \texttt{coadd} image in each band.
    This forced photometry approach is optimized to yield accurate galaxy colours
    at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{HSC-PIPE}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
    photometry, which means that it can accurately measure both the 
    \textit{fluxes and colours of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the 
    point spread function (PSF). 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{}, as it is incapable of
    modelling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, it is challenging to accurately 
    deblend in the vicinity of large ETGs, where satellites and background galaxies 
    often blend with the low surface brightness stellar envelope. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    `over-deblend' the outskirts of bright galaxies and leads to an 
    underestimation of the total flux of massive ETGs. (This is discussed further in 
    \citealt{HSC-PIPE}.)   
    For these reasons, our results are based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    (1) to perform a first broad sample selection, and (2) to estimate the average 
    colour of massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Initial massive galaxy sample}
    \label{ssec:initial}
